A re-examination of the role of friction in the original Social Force Model

### 2019-05-21 paper.tex
corregi hasta punto 6 de referee 2

\textcolor{red}{The measurements were taken once the system reached the 
stationary state ($t=30$~s), while the configurations of the systems were 
recorded every 0.05~s, that is, at intervals as short as 10\% of the 
pedestrian’s relaxation time (see Section. \ref{sfm}). The recorded magnitudes 
were the pedestrian’s positions and velocities for each process. We also 
computed the clustering structures using a LAMMPS built in function 
\textcolor{blue}{(named compute cluster-atom)}}.\\

>>>>

\textcolor{red}{The measurements were taken once the system reached the 
stationary state ($t=30$~s), while the configurations of the systems were 
recorded every 0.05~s, that is, at intervals as short as 10\% of the 
pedestrian’s relaxation time (see Section. \ref{sfm}). The recorded magnitudes 
were the pedestrian’s positions and velocities for each process. We also 
computed the clustering structures using a LAMMPS built in function 
named compute cluster-atom. This function assigns each pedestrian a cluster ID.
A cluster is defined as a set of pedestrians, each of which is within the cutoff
distance from one or more other pedestrians in the cluster. 
If a pedestrian has no neighbors within the cutoff distance, then it is a 1-pedestrian cluster.}\\
